The Astropy Project

### 2017-10-18 main.tex
typo

The \package{visualization} package provides functionality that can be helpful when visualizing data. This includes a framework for plotting astronomical images with coordinates with Matplotlib (previously the standalone \package{wcsaxes} package), functionality related to image normaliation (including both scaling and stretching), smart histogram plotting, RGB color image creation from separate images, and custom plotting styles for Matplotlib.

>>>>

The \package{visualization} package provides functionality that can be helpful when visualizing data. This includes a framework for plotting astronomical images with coordinates with Matplotlib (previously the standalone \package{wcsaxes} package), functionality related to image normalization (including both scaling and stretching), smart histogram plotting, RGB color image creation from separate images, and custom plotting styles for Matplotlib.
